---
title: "Midterm - Q3"
output: html_document
date: "2022-10-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
a. Importing the dataset and reading it on csv
```{r}
library(readr)
Titanic <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")
Titanic
```
b. Median age-determining the median age for by passenger class
```{r}
library(dplyr)
summary(Titanic) # checking out my dataset to get an idea of the distributions of variables
Titanic %>% group_by(Pclass) %>% summarise(Median_age=median(Age))# code for determining the median age for by passenger class
```

c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. 

I used boxplot to show medians, spread of data, and outliers for the continuous variable age according to passenger class
```{r}
boxplot(Titanic$Age~Titanic$Pclass, ylab = "Age",
        xlab = "Pclass", main = "Age According to Passenger Class")


```

Code to determine the percentage of males and females by class

```{r}
Titanic %>% group_by(Pclass, Sex) %>% 
    summarise(Sex = n()) %>%
  mutate(freq = round(Sex / sum(Sex), 3)*100)
```
